Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 study_workload_1.tex
tweak in Section 4

The study of Workload~\Rmnum{1} consists of two parts. First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations. Second, we isolate each application from the workload and analyze its performance on both a per-rank basis as well as by considering router traffic resident to application ranks. The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.

@@

%Explain RM
In most cases for this study, the random placement policy behaves similarly across routing policies.
Random placement uniformly distributes MPI ranks over the network, 
balancing the resulting traffic load. 
As shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
no router experiences an exceptionally high volume of traffic on its local and global channels. 
When random placement is coupled with minimal routing (RM), less traffic is generated on account of
the packets avoiding intermediate forwarding. At the same time, there is still significant congestion on local channels due to the lack of ability of packets to traverse non-minimal routes, falling into the same trap as the contiguous-minimal configuration.
%\TODO{check this}
%Explain RA, RPA
Coupled with (progressive) adaptive routing,
saturation times are effectively minimized on both global and local channels when random placement is in use, 
as shown in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. Further, in comparison to contiguous allocations, random allocations result in a more evenly distributed load on the resulting channels, as expected.

% Explain terminal link traffic and busy time
Figures~\ref{fig:terminal-link-traffic} and \ref{fig:terminal-link-stime} are presented for the purpose of symmetry, 
showing the traffic per terminal link as well as the saturation time experienced at each terminal.
The terminal traffic distribution corresponds directly to application traffic, as we are using one MPI rank per node (terminal).
However, saturation times are different, resulting from the aforementioned network behavior. Particularly, contiguous allocations coupled with minimal routing results in a ``long-tail`` distribution of saturation time.

@@

The AMG application (Figure~\ref{fig:amg-commtime}), however, shows markedly
different behavior when using random allocation. Random allocation with minimal
routing results in worse performance than contiguous-adaptive configurations,
while using adaptive routing results in significant performance regressions. As
this is a counterintuitive result not reached by other works, we investigate
further.

@@

The system behavior with respect to the CrystalRouter application arguably best
matches expectations. Use of contiguous allocations result in a subset of
channels with a significant traffic load while a significant portion are
unused. Use of random allocations result in a comparatively smoother traffic
distribution, with some variation on the margins due to the randomness.

>>>>

The study of Workload~\Rmnum{1} consists of two parts. First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations. Second, we isolate each application from the workload and analyze its performance both on a per-rank basis as well as by considering router traffic resident to application ranks. The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.

@@

%Explain RM
In most cases, the random placement policy behaves similarly across routing policies.
Random placement uniformly distributes MPI ranks over the network, 
balancing the resulting traffic load. 
As shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
no router experiences an exceptionally high volume of traffic on its local and global channels. 
When random placement is coupled with minimal routing (RM), less traffic is generated on account of
the packets avoiding intermediate forwarding. At the same time, there is still significant congestion on local channels due to the lack of ability of packets to traverse non-minimal routes, falling into the same trap as the contiguous-minimal configuration.
%\TODO{check this}
%Explain RA, RPA
Coupled with (progressive) adaptive routing,
saturation times are effectively minimized on both global and local channels when random placement is in use, 
as shown in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. Further, in comparison to contiguous allocations, random allocations result in a more evenly distributed load on the resulting channels, as expected.

% Explain terminal link traffic and busy time
Figures~\ref{fig:terminal-link-traffic} and \ref{fig:terminal-link-stime} are presented for the purpose of symmetry, 
showing the traffic per terminal link as well as the saturation time experienced at each terminal.
The terminal traffic distribution corresponds directly to application traffic, as we are using one MPI rank per node (terminal).
However, saturation times are different, resulting from the aforementioned network behavior. Particularly, contiguous allocations coupled with minimal routing results in a ``long-tail" distribution of saturation time.

@@

The AMG application (Figure~\ref{fig:amg-commtime}), however, shows markedly
different behavior when using random allocation. Random allocation with minimal
routing results in worse performance than contiguous-adaptive configurations,
while using adaptive routing results in significant performance regressions. As
this is a counterintuitive result not discussed in other works, we investigate
further.

@@

The system behavior with respect to the CrystalRouter application arguably best
matches expectations. Use of contiguous allocations results in a subset of
channels with a significant traffic load while a significant portion are
unused. Use of random allocations results in a comparatively smoother traffic
distribution, with some variation on the margins due to the randomness.
